### 2014-10-08 fundamentals/impl.tex
remove a few therefores and be consisteng about plug-in vs plugin

Agent plug-ins utilize the generic core API to interact with one another. 
Mainly they do this by trading resources.

@@

A key innovation that has previously not been implemented in nuclear fuel cycle 
simulators in the literature is implementing this generic API and modular 
architecture into a suite of dynamically loadable ``plug-in'' libraries. 
This is implemented largely through a clean API and a modern build system.

Dynamically-loadable libraries are the primary mechanism for extending \Cyclus' capability. 
This approach provides encapsulation: the core of the code operates
completely independently from the individual libraries. Thus, any
customization or extension is implemented only in the loadable
library.

This approach allows efficient, targeted contribution to the ecosystem of libraries.  The 
scientist-developer can therefore focus on generating a model within their 
sphere of expertise, while relying on the model contributions of others to fill 
in the other technologies.  This strategy also allows individual developers to
explore different levels of complexity within their archetypes, including
wrapping other simulation tools as loadable libraries within the \Cyclus
framework.

@@

In particular, since the clean plug-in architecture loads libraries without any
modifications to the \Cyclus kernel, closed-source archetypes can be used with
the simulator alongside open-source archetypes. This architecture therefore
allows closed-source libraries (e.g., those representing sensitive nuclear
processes and subject to export control) to be developed and licensed privately.

@@

A key compontent of the \Cyclus kernel architecture is the ability for
implementations of actors in a given simulation to be easily
interchanged. Critically, this novel functionality enables the comparison
between agent implementations. For example, a low-physics-fidelity
implementation of a reactor can be comparied to an implementation with higher
physics fidelity, allowing an analyst to discern the effect of reactor physical
fidelity on a given fuel cycle.

>>>>

Agent plugins utilize the generic core API to interact with one another. 
Mainly they do this by trading resources.

@@

A key innovation that has previously not been implemented in nuclear fuel cycle 
simulators in the literature is implementing this generic API and modular 
architecture into a suite of dynamically loadable ``plugin'' libraries.
This is implemented largely through a clean API and a modern build system.

Dynamically-loadable libraries are the primary mechanism for extending \Cyclus' capability. 
This approach provides encapsulation: the core of the code operates
completely independently from the individual plugin libraries. Thus, any
customization or extension is implemented only in the loadable
library.

This approach allows efficient, targeted contribution to the ecosystem of libraries.  The 
scientist-developer can focus on generating a model within their
sphere of expertise, while relying on the model contributions of others to fill 
in the other technologies.  This strategy also allows individual developers to
explore different levels of complexity within their archetypes, including
wrapping other simulation tools as loadable libraries within the \Cyclus
framework.

@@

In particular, since the clean plugin architecture loads libraries without any
modifications to the \Cyclus kernel, closed-source archetypes can be used with
the simulator alongside open-source archetypes. This architecture
allows closed-source libraries (e.g., those representing sensitive nuclear
processes and subject to export control) to be developed and licensed privately.

@@

A key compontent of the \Cyclus kernel architecture is the ability for
implementations of actors in a given simulation to be easily
interchanged. Critically, this novel functionality enables the comparison
between agent implementations. For example, a low-physics-fidelity
implementation of a reactor can be compared to an implementation with higher
physics fidelity, allowing an analyst to discern the effect of reactor physical
fidelity on a given fuel cycle.
